Paper notes

### 2019-08-05 paper_notes.Rmd
OK logistic regression

prob <- function(e_w,v_w,d_u_e,d_u_v){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}

@@

value_mean_neighborhood <- seq(0.0, 1.0, by = 0.1)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
name <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility",  main = "Value Utility for neighborhood j of agent i",  sub = name)

report_v <- paste0(name,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)

@@

# prob <- function(e_w,s,t,v_w,p,q){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}

@@

prob1 <- prob(100,300,100,1,100,100)

plot(prob1)
```

>>>>

@@

value_mean_neighborhood <- seq(0.0, 1.0, by = 0.1)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)

report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)

@@

# prob <- function(e_w,v_w,d_u_e,d_u_v){1 / (1 + exp(-e_w*(d_u_e)) + exp(-v_w*(d_u_v)))}

@@

prob <- function(d_u_e,d_u_v,par_e,par_v){round(1 / (1 + exp(-par_e*(d_u_e) + (-par_v*(d_u_v)))),digits= 2)}

e_w <- 0.2
v_w <- (1 - e_w)

par_e <- 0
par_v <- 10-par_e

d_u_e <- -1

  dis_0   <- prob(d_u_e,0.0,par_e,par_v)
  dis_0.1 <- prob(d_u_e,0.1,par_e,par_v)
  dis_0.2 <- prob(d_u_e,0.2,par_e,par_v)
  dis_0.3 <- prob(d_u_e,0.3,par_e,par_v)
  dis_0.4 <- prob(d_u_e,0.4,par_e,par_v)
  dis_0.5 <- prob(d_u_e,0.5,par_e,par_v)
  dis_0.6 <- prob(d_u_e,0.6,par_e,par_v)
  dis_0.7 <- prob(d_u_e,0.7,par_e,par_v)
  dis_0.8 <- prob(d_u_e,0.8,par_e,par_v)
  dis_0.9 <- prob(d_u_e,0.9,par_e,par_v)
  dis_1   <- prob(d_u_e,1.0,par_e,par_v)
  dis_0.1neg <- prob(d_u_e,-0.1,par_e,par_v)
  dis_0.2neg <- prob(d_u_e,-0.2,par_e,par_v)
  dis_0.3neg <- prob(d_u_e,-0.3,par_e,par_v)
  dis_0.4neg <- prob(d_u_e,-0.4,par_e,par_v)
  dis_0.5neg <- prob(d_u_e,-0.5,par_e,par_v)
  dis_0.6neg <- prob(d_u_e,-0.6,par_e,par_v)
  dis_0.7neg <- prob(d_u_e,-0.7,par_e,par_v)
  dis_0.8neg <- prob(d_u_e,-0.8,par_e,par_v)
  dis_0.9neg <- prob(d_u_e,-0.9,par_e,par_v)
  dis_1neg   <- prob(d_u_e,-1.0,par_e,par_v)

  value_difference <- seq(-1.0,1.0, by = 0.1)
  prob_choice <- c(dis_1neg,dis_0.9neg,dis_0.8neg,dis_0.7neg,dis_0.6neg,dis_0.5neg,dis_0.4neg,dis_0.3neg,dis_0.2neg,dis_0.1neg,dis_0,dis_0.1,dis_0.2,dis_0.3,dis_0.4,dis_0.5,dis_0.6,dis_0.7,dis_0.8,dis_0.9,dis_1)

  name_diff <- paste0("Ethnic Difference New - Old = ",d_u_e,"Ethnic parameter = ", par_e, "Value parameter = ", par_v, 
                      "\r\n Utility Difference -1 = MIN Utility Alternative, 1 = MAX Utility Alternative")

plot(value_difference,prob_choice,xlab = "Value Difference Alternative - Current \r\n",ylab = "probability to choose alternative", main = "Probability to choose alternative", sub = name_diff)
